Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated

### 2016-12-22 ms_pre_post.Rmd
Add some new degeneracy citations

Another general inference from our model concerns the dynamics of phenotypes with highly overlapping effects with respect to selection, as realised through functionally different traits. Pre-copulatory inbreeding avoidance, typically expressed through mating behaviour, versus post-copulatory inbreeding avoidance, typically expressed through phenotypes affecting fertilisation, are both driven by the shared selective pressure of inbreeding depression in offspring viability. Hence, evolution of each of these strategies might make the other strategy more or less adaptive by modifying its impact on the degree to which a female avoids inbreeding and consequently has offspring that express inbreeding depression. The ability of structurally different phenotypes to perform the same adaptive function is an example of 'degeneracy', a term which defines a more general phenomenon whereby unique elements of a system result in identical outputs [@Edelman2001].

>>>>

Another general inference from our model concerns the dynamics of phenotypes with highly overlapping effects with respect to selection, as realised through functionally different traits. Pre-copulatory inbreeding avoidance, typically expressed through mating behaviour, versus post-copulatory inbreeding avoidance, typically expressed through phenotypes affecting fertilisation, are both driven by the shared selective pressure of inbreeding depression in offspring viability. Hence, evolution of each of these strategies might make the other strategy more or less adaptive by modifying its impact on the degree to which a female avoids inbreeding and consequently has offspring that express inbreeding depression. The ability of structurally different phenotypes to perform the same adaptive function is an example of 'degeneracy', a term which defines a more general phenomenon whereby unique elements of a system result in identical outputs [@Edelman2001]. Effects of degeneracy can be observed across nearly all biological scales [@Edelman2001], including complex systems affecting organismal development [e.g., @Nowak1997], adaptation [@Whitacre2010; @Whitacre2010a], and cognition [@Price2002; @Park2013], as well as population [@Atamas2009] and ecosystem [e.g., @Levin2008] dynamics. The relevance of degeneracy with respect to reproductive strategies requires further theoretical development, and might potentally result in new empirical predictions and conceptual synthesis across biological scales.
